Poster Data Analysis

### 2018-09-12 notebooks/poster_analysis.Rmd
updated color scheme on heatmap plot

## Minimum Spanning Tree of MLST profiles
Minimum spanning tree of sequence types, created in Phyloviz[3] with goeBURST distance (TLV). Light blue = Broiler, dark blue = Pig, light green = Red fox, and dark green = Wild bird. Distances between sequence types are denotd as numbers on the lines. 
![](../figures/mlst_tree_full.png)

@@

# Plot the heatmap
p2 <- ggplot(heatmap_data, aes(fct_reorder(gene, type2),
             factor(id),
             fill = fillcol,
             alpha = result)) +
  geom_tile(color = "white")+
  geom_vline(xintercept = 13.5)+
  scale_fill_brewer(palette = "Paired",
                    na.value = "#6b6767")+
  theme_minimal()+
  labs(fill = NULL)+
  theme(axis.text.x = element_text(angle = 90,
                                   hjust = 1,
                                   vjust = 0.3,
                                   size = 7),
        axis.title = element_blank(),
        axis.text.y = element_blank(),
        panel.grid = element_blank(),
        legend.position = "right")+
  guides(alpha = FALSE)+
  coord_fixed()

>>>>

## Minimum Spanning Tree of MLST profiles
Minimum spanning tree of sequence types, created in Phyloviz[3] with goeBURST distance. Light blue = Broiler, dark blue = Pig, light green = Red fox, and dark green = Wild bird. Distances between sequence types are denoted as numbers on the lines. 
![](../figures/mlst_tree_full.png)

@@

# Color vector
palette <- c("Broiler_1" = "#a6cee3", "Broiler_0" = "#a6cee326",
             "Pig_1" = "#1f78b4", "Pig_0" = "#1f78b426",
             "Red fox_1" = "#b2df8a", "Red fox_0" = "#b2df8a26",
             "Wild bird_1" = "#33a02c", "Wild bird_0" = "#33a02c26")

# Plot the heatmap
p2 <- ggplot(heatmap_data, aes(fct_reorder(gene, type2),
             factor(id),
             fill = fillcol)) +
  geom_tile(color = "white")+
  geom_vline(xintercept = 13.5)+
  scale_fill_manual(values = palette,
                    na.value = "#6b6767")+
  theme_minimal()+
  labs(fill = NULL)+
  theme(axis.text.x = element_text(angle = 90,
                                   hjust = 1,
                                   vjust = 0.3,
                                   size = 7),
        axis.title = element_blank(),
        axis.text.y = element_blank(),
        panel.grid = element_blank(),
        legend.position = "right")+
  guides(fill = guide_legend(reverse = TRUE))+
  coord_fixed()
